%% Example CV - Rasika Deodhar
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Rasika Deodhar - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Rasika}{Deodhar}
\address{St. Paul, Minnesota, USA}{}{}
\phone[mobile]{+1-612-356-8720}
\email{rasikadeodhar95.12@gmail.com}
\extrainfo{\href{https://linkedin.com/in/rasika-deodhar}{LinkedIn}, \href{https://github.com/Rasika-Deodhar}{GitHub}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{AI/GenAI engineer and AI program manager with a full-stack development foundation. Built and deployed LLM-powered products (RAG document extraction, an internal chatbot, TTS/STT APIs) as an Applications Developer at MMC Innovation Lab, then moved into AI-driven automation and self-service workflow design (n8n, Salesforce) as an AI Program Management Intern at Qlik. Pairs hands-on technical depth with a Master's in Engineering Management (GPA 4.0, expected Dec 2026) and a Certified AI-Empowered SAFe Agilist credential.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Gen AI / LLM Engineering}: Prompt engineering, RAG, LangChain, OpenAI GPT, Llama, Hugging Face Transformers, vector databases (Pinecone, Chroma, Weaviate, Qdrant)

\item \textbf{Full-Stack Development}: Python, JavaScript/TypeScript, React/Next.js, Node.js, Java 8/Spring Boot, Angular 9+ (RxJS, NgRx), REST/GraphQL APIs

\item \textbf{AI Automation \& Program Management}: n8n, Salesforce, Agile/Kanban delivery, cross-functional stakeholder collaboration, Certified AI-Empowered SAFe Agilist

\item \textbf{Cloud \& DevOps}: Docker, Kubernetes (basics), AWS (EC2/S3/Lambda), GCP, CI/CD (GitHub Actions, Jenkins)

\item \textbf{Data \& Enterprise Architecture}: MongoDB, SQL, PostgreSQL, business alignment, strategic planning, technology evaluation, governance \& standards

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Most Recent Role ---
\item{\cventry{2026--Present}{AI Program Management Intern}{Qlik}{St. Paul, Minnesota}{}{\vspace{1pt}
\begin{itemize}
    \item Building AI agent workflows and automation pipelines using n8n and Salesforce to shift post-sales customer support toward a self-service model, reducing dependency on live agents for help desk resolution.
\end{itemize}}}

\vspace{3pt}

% --- Previous Role ---
\item{\cventry{2022--2024}{Applications Developer}{MMC Innovation Lab}{Dublin, Ireland}{}{\vspace{1pt}
\begin{itemize}
    \item Contributed to a company-wide LLM-powered chatbot (LenAI) and document extraction workflows using prompt engineering and RAG, reducing manual data entry time by 40\%.
    \item Built and tested PoC applications with OpenAI GPT models, Llama, LangChain, and vector databases (Pinecone/Chroma), accelerating the internal R\&D cycle by 3 weeks.
    \item Designed and published internal APIs for Text-to-Speech and Speech-to-Text services via Google Apigee, supporting 10k+ monthly API calls across multiple teams.
    \item Conducted hands-on workshops and created reusable prompts/templates, onboarding 100+ employees to the GenAI framework.
\end{itemize}}}

\vspace{3pt}

% --- Earlier Role ---
\item{\cventry{2020--2022}{Technology Analyst}{Citi}{Dublin, Ireland}{}{\vspace{1pt}
\begin{itemize}
    \item Developed and maintained full-stack features for a global scaled application using Java 8, Spring Boot, Angular 9/10, and Oracle DB, improving system throughput by 20\%.
    \item Led UI migration from legacy systems to Angular, resulting in a 40\% decrease in page load times.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{2025--Expected 2026}{Master's in Engineering Management}{St. Cloud State University}{Minnesota, USA}{}{\vspace{1pt}
GPA: 4.0. Coursework: AI for Engineering Managers, Quality Engineering, Engineering Project Management, Supply Chain \& Logistics, Lean Six Sigma.
}}

\vspace{3pt}

\item{\cventry{2012--2017}{Bachelor of Engineering, Information Technology}{The University of Pune}{Pune, India}{}{\vspace{1pt}
GPA: 3.60, First Class with Distinction.
}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Hindi (native), Marathi (native), English (professional).
\end{itemize}

% ============================================================
%     HONORS AND AWARDS
% ============================================================

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{Certified AI-Empowered SAFe Agilist} -- Scaled Agile, Inc. (valid until April 2027).}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
